---
title: "data manipulation hands-on"
author: "YOUR_NAME_HERE"
date: "`r Sys.Date()`"
output: word_document
---

```{r}
library(PKPDmisc)
library(knitr)
library(tidyverse)
```

## DATA IMPORT

Objectives:

* Import datasets and documents
* Perform basic data manipulation upon importing the data.

### Task-I

Use the .csv files `demog`, `IV`, and `Oral` provided into the data object folder. 

1. Read in all three csv files  and give them descriptive names (not data1, data2, data3)


## DATA MANIPULATION
The goals of this section:

* Use data manipulation tools to prepare the dataset for analysis

### Task-II
1.  Rename "DV" column as "COBS"

2. Add a Formulation column and label IV/Oral for each dataset

3. Create one integrated dataset with both IV and Oral data.

4. Appropriately merge the demographics dataset into the IV and Oral dataset

5. Perform the following tasks:
    a. Ensure that the following columns are numeric and not text: TIME, COBS, WT, AGE, AMT and DOSEs
    b. Change the following:
    c. Create a new column called BQLFLAG which takes a value of "0" if there is a numerical value in CObs and "1" if there is "BQL" in CObs.
    d. Filter the dataset such that you remove all rows where BQLFLAG=1
        i. WT from lb to kg 
    e. Create a new column called "GENDER" where:
        i. Female = 0
        ii. Male = 1 
    f. Create a new column called RACEN where:
        i. Caucasian = 0
        ii. Asian = 1
        iii. Black = 2
        iv. Hispanic = 3
    g. Create a new column called "USUBJID" - unique subject ID as combination of formulation and ID (hint check out `?interaction`)
    h. Remove the following columns
        i. SEX
        ii. RACE
6. Save the above modifications as a new csv file

## Descriptive Statistics

Objectives

* How to make summaries of the data using descriptive statistics and other data manipulation tools (dplyr, base R functions etc)

### Task III

```{r}

```

1. show a summary for all demographic columns


2. Count the number of males/females in the dataset

3. Count the number of subjects in each "Race" category

4. calculate the min, mean, and max values for WT, AGE:
    a. by Gender
    b. by Race
    
5. What is the Average numbers samples(observations) per individual in this dataset. Hint: make sure you are *only* counting samples, not necessarily all rows are observations!

6. Calculate the Mean, 5th, and 95th percentile concentration at each time point for each formulation and dose level. hint: you can use `?quantile` to calculate various quantiles
