---
title: "data manipulation hands-on"
author: "YOUR_NAME_HERE"
date: '`r Sys.Date()`'
output:
  html_document: default
  word_document: default
---

```{r}
library(PKPDmisc)
library(knitr)
library(tidyverse)
```

## DATA IMPORT

Objectives:

* Import datasets and documents
* Perform basic data manipulation upon importing the data.

### Task-I

Use the .csv files `demog`, `IV`, and `Oral` provided into the data object folder. 

1. Read in all three csv files  and give them descriptive names (not data1, data2, data3)

```{r, message = FALSE, warning=FALSE}
iv_dat <- read_csv("../../data/IV.csv") %>% mutate(FORM = "IV")
oral_dat <- read_csv("../../data/Oral.csv") %>% mutate(FORM = "Oral")
demog <- read_csv("../../data/demog.csv") 
```

## DATA MANIPULATION
The goals of this section:

* Use data manipulation tools to prepare the dataset for analysis

### Task-II
1.  Rename "DV" column as "COBS"

2. Add a Formulation column and label IV/Oral for each dataset

3. Create one integrated dataset with both IV and Oral data.

4. Appropriately merge the demographics dataset into the IV and Oral dataset

```{r}
pk_dat <- bind_rows(iv_dat, oral_dat)
all_dat <- left_join(pk_dat, demog)
```


5. Perform the following tasks:
    a. Ensure that the following columns are numeric and not text: TIME, COBS, WT, AGE, AMT and DOSEs
    
```{r}
all_dat_cleaned <- all_dat %>% 
  mutate(BQLFLAG = ifelse(is.na(DV), 0, 
                          ifelse(DV == "BQL", 1, 0))) 

```

    
    b. Change the following:
    c. Create a new column called BQLFLAG which takes a value of "0" if there is a numerical value in CObs and "1" if there is "BQL" in CObs.
    d. Filter the dataset such that you remove all rows where BQLFLAG=1

```{r}
all_dat_no_bql <- all_dat_cleaned %>% 
  filter(BQLFLAG != 1) %>%
  mutate(WTlbs = WT*2.2,
         GENDER = ifelse(SEX == "Female", 0, 1),
         RACEN = ifelse(RACE == "Caucasian", 0,
                        ifelse(RACE == "Asian", 1,
                               ifelse(RACE == "Black", 2, 
                                      ifelse(RACE == "Hispanic", 3, -99)))),
         USUBJID = paste(ID, FORM, sep = ""))
head(all_dat_no_bql)
```

```{r include = F}
if (any(all_dat_no_bql$RACEN == -99)) {
  stop("a non-handled race variable was detected")
}
```

    
    
    
        i. WT from lb to kg 
    e. Create a new column called "GENDER" where:
        i. Female = 0
        ii. Male = 1 
    f. Create a new column called RACEN where:
        i. Caucasian = 0
        ii. Asian = 1
        iii. Black = 2
        iv. Hispanic = 3
    g. Create a new column called "USUBJID" - unique subject ID as combination of formulation and ID (hint check out `?interaction`)
    h. Remove the following columns
        i. SEX
        ii. RACE
6. Save the above modifications as a new csv file

## Descriptive Statistics

Objectives

* How to make summaries of the data using descriptive statistics and other data manipulation tools (dplyr, base R functions etc)

### Task III

```{r}

```

1. show a summary for all demographic columns

```{r}
demog_final <- all_dat_no_bql %>% 
  distinct(ID, FORM, .keep_all = T)

demog_final %>% 
  select(SEX:RACE) %>% 
  mutate(SEX = as.factor(SEX),
          RACE= as.factor(RACE)) %>% 
  summary
```


2. Count the number of males/females in the dataset

```{r}
demog_final %>% count(SEX, GENDER, FORM)

demog_final %>% group_by(SEX, GENDER, FORM) %>% tally
demog_final %>% 
  group_by(SEX, GENDER, FORM) %>% 
  summarize(n = n())
```


3. Count the number of subjects in each "Race" category

4. calculate the min, mean, and max values for WT, AGE:
    a. by Gender
    b. by Race
    
5. What is the Average numbers samples(observations) per individual in this dataset. Hint: make sure you are *only* counting samples, not necessarily all rows are observations!

6. Calculate the Mean, 5th, and 95th percentile concentration at each time point for each formulation and dose level. hint: you can use `?quantile` to calculate various quantiles
