---
title: "diagnostic-plots"
author: "YOUR_NAME_HERE"
date: "`r Sys.Date()`"
output: html_document
---


1) read in the csv datasets:

* EtaCov_gathered
* Residuals
* Theta

```{r libraries}
library(PKPDmisc)
library(knitr)
library(ggplot2)
library(dplyr)
library(tidyr)
```

```{r readdata}
# read all data in this chunk
```

2) From the Theta table, create a reasonable quality output table of the results.
Hint, use knitr::kable, in combination with results='asis' in the chunk settings

requires names:

```{r}

```


* clean up columns
* clean up column names
* units

3) Create a CWRES vs Time plot with loess fits for the central tendency and the spread (hint abs() is your friend for the spread)

```{r}

```

4) update the CWRES vs Time plot to flag anything with CWRES > 2.5 as a red value
```{r}

```

5) print a table of key information for all points with CWRES > 3

```{r, results ='asis'}

```


6) Plot individual IPRED and DV vs time

```{r}

```


6b) add the population prediction as a dashed blue line

```{r}

```

7) With EtaCov_final create histograms of all the eta distributions

```{r}

```

BONUS: add a mean value for each eta overlaid on the above plot
```{r}

```

8) Create Eta vs Covariate plots for each covariate and all etas

```{r}

```


Individual method:

For small numbers of covariates, can create a plot for each
```{r}

```

Hint: since there is so much duplicated, this would be a good opportunity to turn that into a function that you pass in the covariate to plot for `x`.

9) add loess fits to the eta cov plots

```{r}

```

